Hybrid oddball - SSVEP BCI

### 2013-04-10 draftHybridPaper/draftHybridBCI.tex
minor update

@@

\begin{abstract}
Objectives:

Results:

@@

@@

    % EEG acq
    The EEG signals were recorded using a BioSemi Active Two system with 32~channels (following the 10-20 international system) at a sampling rate of \SI{1024}{\Hz}.
    Two additional electrodes were positioned on the right and left mastoids and the mean of the signals recorded at those two sites was used as reference for the 32~EEG electrodes.

    % Stimuli presentation
    All recordings and stimulation employed MATLAB\textsuperscript{\textregistered}, the stimuli were visually presented on a laptop's LCD screen (\SI{60}{\Hz} refresh rate) and their display and timing used the \emph{Psychophysics Toolbox Extensions} (\cite{Brainard1997,Pelli1997}).

@@

        % Aim and subjects
        The aim of this first experiment was to study the effect of a flickering background on the typical ERP response associated to an oddball-based BCI.
        N subjects participated in the experiment (age, gender).

        % exp description
        As shown in \autoref{fig:stimSeq}, a typical \emph{stimulation cycle}, started with a \SI{2000}{\ms} cue, indicating the participant his/her target item, followed by a \SI{1000}{\ms} pause during which the cue disappears and all icons remained gray.
        The background rectangle would then start to flicker and the oddball stimulation would start after \SI{500}{\ms}.
        The oddball stimulation consisted of 10~\emph{flashing sequences} during which each of the 6~icons was flashed one after another in random order for a duration randomly set between \SIlist[list-units = single]{200;300}{\ms}.
        As usually done for oddball experiments, the participants were instructed to focus on their target symbol and count the number of time it flashes.
        A \SI{1000}{\ms} pause followed the oddball stimulation and preceded the next cue.
        An \emph{experimental run} consisted of 12 consecutive stimulation cycles, so that each of the 6~icons was cued twice (in random order) and lasted approximately 4~minutes.

@@

        % use
        The data collected were used to compare the shape of the oddball response (response to the flashing of the target icon) and the ERP classification accuracy (response to target \emph{v.s.} response to non-target flasing) across condition.

@@

    \subsection{Experiment 2: studying the SSVEP responses}
    \label{sec:2.3SSVEP}

@@

        % Aim and subjects
        The aim of this second experiment was to study the effect of an oddball paradigm on the SSVEP responses.
        N subjects participated in the experiment (age, gender).

@@

        % use
        This experimental design allows a comparison of the SSVEP responses of the participants with and without an oddball stimulation superimposed on the SSVEP stimulation for a different set of SSVEP frequencies.

@@

@@

    \subsection{Experiment 2: studying the SSVEP responses}
    \label{sec:2.3SSVEP}

@@

>>>>

\acrodef{SSVEP}{Steady-State Visually Evoked Potential}
\acrodef{BCI}{Brain-Computer Interface}

@@

\begin{abstract}
Objectives:
blablabla blalabbla \ac{SSVEP}-based BCIs.

Results:
blablabla blablabla \ac{SSVEP} responses.

@@

\acresetall

@@

    % EEG acq
    The EEG signals were recorded using a BioSemi Active Two system with 32~channels (following the 10-20 international system) at a sampling rate of \SI{1024}{\Hz}.
    Two additional electrodes were positioned on the right and left mastoids and the mean of the signals recorded at those two sites was used to reference the activity measured by the 32~EEG electrodes.

    % Stimuli presentation
    All stimulation employed MATLAB\textsuperscript{\textregistered}, the stimuli were visually presented on a laptop's LCD screen (\SI{60}{\Hz} refresh rate) and their display and timing used the \emph{Psychophysics Toolbox Extensions} (\cite{Brainard1997,Pelli1997}).

@@

        % Aim and subjects
        The aim of this first experiment was to study the effect of a flickering background on the typical ERP response associated to an oddball paradigm.
        N subjects participated in the experiment (age, gender).

        % exp description
        As shown in \autoref{fig:stimSeq}, a typical \emph{stimulation cycle}, started with a \SI{2000}{\ms} cue, indicating the participant his/her target item, followed by a \SI{1000}{\ms} pause during which the cue disappears and all icons remained gray.
        The background rectangle then started to flicker and the oddball stimulation started \SI{500}{\ms} later.
        The oddball stimulation consisted of 10~\emph{flashing sequences} during which each of the 6~icons was flashed one after another in random order for a duration randomly set between \SIlist[list-units = single]{200;300}{\ms}.
        As usually done for oddball experiments, the participants were instructed to focus on their target symbol and count the number of time it flashes.
        A \SI{1000}{\ms} pause followed the oddball stimulation and preceded the next cue.
        An \emph{experimental run} lasted approximately 4~minutes and consisted of 12 consecutive stimulation cycles, so that each of the 6~icons was cued twice (in random order).

@@

        % use
        The data collected were used to compare the shape of the oddball response (response to the flashing of the target icon) and the ERP classification accuracy (response to target \emph{v.s.} response to non-target flasing) across conditions.

@@

    \subsection{Experiment 2: studying the \acs{SSVEP} responses}
    \label{sec:2.3SSVEP}

@@

        % Aim and subjects
        The aim of this second experiment was to study the effect of an oddball paradigm on the \ac{SSVEP} responses.
        N subjects participated in the experiment (age, gender).

@@

        The experiment consisted thus of 8~runs of approximately 4~minutes each.
        The order of the run was randomized for each subject and a 5~to~10~minutes pause was set up after the first 4~runs.

        % use
        This experimental design allows a comparison of the \ac{SSVEP} responses of the participants with and without an oddball stimulation superimposed on the \ac{SSVEP} stimulation for a different set of \ac{SSVEP} frequencies.

@@

        % pre-processing

        % snr calculation

        % statistics

@@

    \subsection{Experiment 2: studying the \ac{SSVEP} responses}
    \label{sec:2.3SSVEP}

@@

%\section{Acronyms}
%\begin{acronym}
%    \acro{SSVEP}{Steady-State Visually Evoked Potential}
%\end{acronym}
